Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-14 write-ups/PLDI/paper.tex
Fix compilation

Cooperative multitasking was offered in ancient operating systems
(e.g. Windows before the 95 edition) and is still used nowadays in
RISC OS for instance. In the context of GPU resources, cooperative
multitasking seems to refer to sizing kernels such that they do not
compute for too long in order to yield the whole GPU
regularly~\cite{adriaens2012case}. Our contribution present a much
more flexible cooperative multitasking, where the long-running
application is never totally stopped.

>>>>

Cooperative multitasking was offered in ancient operating systems
(e.g. Windows before the 95 edition) and is still used nowadays in
RISC OS for instance. Many programming languages offer cooperative
multitasking via variations of coroutines, e.g. coroutine objects in
Python\footnote{\url{https://docs.python.org/3/reference/datamodel.html\#coroutine-objects}}
or Lua\footnote{\url{https://www.lua.org/pil/9.1.html}}, or Ruby's
fiber \footnote{\url{http://ruby-doc.org/core-2.1.1/Fiber.html}}. In
the context of GPU resources, cooperative multitasking seems to refer
to sizing kernels such that they do not compute for too long in order
to yield the whole GPU regularly~\cite{adriaens2012case}. Our
contribution present a much more flexible cooperative multitasking,
where the long-running application is never totally stopped.
